### 2016-08-23 notions.tex
cheers

On the right side of the figure, we give two ``indistinguishability''
notions of privacy.  The first version (ind-qry) captures more
generally what~$M$ and the allowed queries leak about the set that is
represented.  In particular, two sets~$S_0,S_1$ are sampled according
to distribution~$\distr{\calS}{}$, one of these is picked at random to
be represented.  The adversary is provided the resulting~$M,\pubaux$
and allowed to make queries~$q \in \calQ$; it must determine which
of~$S_0$ or~$S_1$ was actually represented.  We call this notion
indistinguishabilty (of sets) under a (adaptively chosen) query
attack.
%
The second version is inspired by the semantic security notion for
encryption schemes, and we refer to it as semantic-security (of sets)
with respect to the full representation (ss-rep).  In this experiment,
a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
and the adversary is given the full ouput of running $\Rep(S)$,
i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.

@@

\medskip
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
$b \getsr \bits$\\
$S_0,S_1 \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
if $b' = b$ then Return 1\\
Return 0\\

\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux,\privaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
Return~$a$\\

@@

\heading{Privacy notions. }
Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
reduction.  We should be able to show
\begin{itemize}
\item ss-rep $\Rightarrow$ ind-qry
\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
\item ind-qry $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ind-qry
\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
    a bit less trivial. I'm sure there are more natural schemes that
    will separate, too.}
\end{itemize}

>>>>

%On the right side of the figure, we give two ``indistinguishability''
%notions of privacy.  The first version (ind-qry) captures more
%generally what~$M$ and the allowed queries leak about the set that is
%represented.  In particular, two sets~$S_0,S_1$ are sampled according
%to distribution~$\distr{\calS}{}$, one of these is picked at random to
%be represented.  The adversary is provided the resulting~$M,\pubaux$
%and allowed to make queries~$q \in \calQ$; it must determine which
%of~$S_0$ or~$S_1$ was actually represented.  We call this notion
%indistinguishabilty (of sets) under a (adaptively chosen) query
%attack.
%
On the right side of the figure, we give a definition
inspired by the semantic security notion for
encryption schemes.  We refer to it as semantic-security (of sets)
with respect to the full representation (ss-rep).  In this experiment,
a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
and the adversary is given the full ouput of running $\Rep(S)$,
i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.

@@

\medskip
\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\pubaux)$\\
if $z \in S$ then Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$
}
}
%
{
\hpagess{.485}{.5}
{
%\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
%$b \getsr \bits$\\
%$S_0,S_1 \getsr \distr{\calS}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
%$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
%if $b' = b$ then Return 1\\
%Return 0\\
%
%\medskip
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$f \getsr A(M,\pubaux,\privaux)$\\
$S' \getsr \distr{\calS}{}$\\
if $f(S) \neq f(S')$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\

@@

\heading{Privacy notions. }
Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
reduction.  We should be able to show
\begin{itemize}
%\item ss-rep $\Rightarrow$ ind-qry
%\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
    a bit less trivial. I'm sure there are more natural schemes that
    will separate, too.}
\end{itemize}

### 2016-08-23 syntax.tex
cheers

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.  Informally, the representation should serve as a good
approximation of the multiset, at least with respect to the allowed
questions.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\Sigma$ is the \emph{representation alphabet}. \jnote{Is
    there any reason not to simply fix this to $\{0,1\}$?}
\item $\Gamma$ is the set of possible \emph{query answers}.
    \jnote{Do we need this for any reason?}
\item $\calS$ is a set  of multisets over universe~$\univ$.
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}.
\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and
    outputting a \emph{representation} $M \in \Sigma^*$,
    \emph{private side information} $\privaux \in \bits^*$, and
    \emph{public side information} $\pubaux \in \bits^*$.
\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $M, \privaux, q$, and returns
    \emph{answer} $a \in \Gamma$. \jnote{Should take $\pubaux$
    as input also.}
\end{itemize}
\hfill\dqed
\end{definition}
\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
Pushing secrets into~$M$ makes it more difficult to capture (for
example) the Neidermeier et al.\ attacks in our privacy notions; see
Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
the bitarray (which one naturally thinks of as~$M$) but not the
secret keys for the PRFs/hash functions.  You could say that the
bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
secret keys, but this is unnatural.} All of the data structures that
we will consider have the property that~$|M|$ does not depend on the
coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
general this need not be true, but the assumption does not restrict
our syntax from capturing natural constructions (e.g., those used in
practice), and it makes it easier to state our security notions.

>>>>

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.  Informally, the representation should serve as a good
approximation of the multiset, at least with respect to the allowed
questions.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\Sigma$ is the \emph{representation alphabet}. \jnote{Is
    there any reason not to simply fix this to $\{0,1\}$?}
\item $\Gamma$ is the set of possible \emph{query answers}.
    \jnote{Do we need this for any reason?}
\item $\calS$ is a set  of multisets over universe~$\univ$.
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}.
\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and
    outputting a \emph{representation} $M \in \Sigma^*$,
    \emph{private side information} $\privaux \in \bits^*$, and
    \emph{public side information} $\pubaux \in \bits^*$.
\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $M, \pubaux,\privaux, q$, and returns
    \emph{answer} $a \in \Gamma$. 
\end{itemize}
\hfill\dqed
\end{definition}
%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
%Pushing secrets into~$M$ makes it more difficult to capture (for
%example) the Neidermeier et al.\ attacks in our privacy notions; see
%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
%the bitarray (which one naturally thinks of as~$M$) but not the
%secret keys for the PRFs/hash functions.  You could say that the
%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
%secret keys, but this is unnatural.} 
All of the data structures that
we will consider have the property that~$|M|$ does not depend on the
coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
general this need not be true, but the assumption does not restrict
our syntax from capturing natural constructions (e.g., those used in
practice), and it makes it easier to state our security notions.
